 
Practical Machine Learning Course Project
==========================================


 I load the data in R (including both training and test data sets).
 ```{r}
 training = read.csv("pml-training.csv", header = TRUE)
 testing = read.csv("pml-testing.csv", header = TRUE)
 ```
 
I look up columns with a high percent of data that is either NA or "", remove entire NA columns, and apply it to data frames.
```{r}
#Remove columns with more than the treshold of NA or "" values
Columns1 <- !apply(training, 2, function(x) sum(is.na(x)) > treshold  || sum(x=="") > treshold)
training <- training[, Columns1]
```

I Partition rows into training and crossvalidation
```{r}
inTrain <- createDataPartition(training$classe, p = 0.6)[[1]]
cv <- training[-inTrain,]
training <- training[ inTrain,]
inTrain <- createDataPartition(cv$classe, p = 0.75)[[1]]
cv_test <- cv[ -inTrain,]
cv <- cv[inTrain,]
```

I train models, pridict and show confusion matrices
```{r}
model1 <- train(classe ~ ., data=training, method="gbm")
model2 <- train(classe ~ ., data=training, method="lda")
predit1 <- predict(model1, cv)
predit2 <- predict(model2, cv)
confusionMatrix(predit1, cv$classe)
confusionMatrix(predit2, cv$classe)
```

I show in-sample error and out-of-sample error
preditDF <- data.frame(predit1, predit2, classe=cv$classe)
combineModFit <- train(classe ~ ., method="rf", data=preditDF)
combPredIn <- predict(combModFit, predDF)
confusionMatrix(combPredIn, predDF$classe)
predDF <- data.frame(pred2, pred3, classe=crossv_test$classe)

I Provide error reports for both training and test data sets.
```{r}

```
